### 2021-05-12 docs/manuscript/PLOS-MSc-Thesis.tex
Remove mention to 714 to avoid confusion
Response to Reviewer #3, 2.b

In order to classify each topology by its subgraph composition, we first created
a matrix  $T = (t_{ij})$ with 714 rows corresponding to each different topology
and 17 columns corresponding to different subgraphs. Each element $t_{ij}$ of
the matrix was 1 if the \emph{j}-th subgraph was present in the \emph{i}-th
topology or 0 if the subgraph was not present.\\

>>>>

In order to classify each topology by its subgraph composition, we first created
a matrix  $T = (t_{ij})$ with \hil{each row} corresponding to \hil{a}
different topology
and 17 columns corresponding to different subgraphs. Each element $t_{ij}$ of
the matrix was 1 if the \emph{j}-th subgraph was present in the \emph{i}-th
topology or 0 if the subgraph was not present.\\
